---
title: "Project1_ZhouxinShi"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

In this project, you’re given a text file with chess tournament results where the information has some structure. Your
job is to create an R Markdown file that generates a .CSV file (that could for example be imported into a SQL database)
with the following information for all of the players:

```{r}
tournament.data <- read.csv(paste0("https://raw.githubusercontent.com/szx868/data607/master/Project1/tournamentinfo.txt"), header=F)
```
### Remove First Few Rows of headings
```{r}
results <- tournament.data[-c(1:3),]
head(results)
```


### Extraction of the columns using regular expressions

```{r}
library(stringr)
player.name <- unlist(str_extract_all(results, "\\w+[^USCF|a-z] ?\\w+ \\w+"))
player.state <- unlist(str_extract_all(results, "(?:^|\\W)ON | MI | OH(?:$|\\W)"))
player.points <- unlist(str_extract_all(results, "\\d\\.\\d"))
pre.rating.step1 <-  unlist(str_extract_all(results, "(R:\\s*)(\\d+)"))
pre.rating.step1[1]
pre.rating <- unlist(str_extract_all(pre.rating.step1, "(\\d+)"))
is.vector(pre.rating)
```


### convert strings to numeric

```{r}
pre.rating <- as.numeric(pre.rating) 
pre.rating[1]
```
```{r}
avg.calc.step1 <- unlist(str_extract_all(results, "\\|[0-9].*"))
avg.calc.step1[16]
avg.calc.step2 <- str_replace_all(avg.calc.step1, "\\s{1,2}\\|","00|")
avg.calc.step2[16]
avg.calc.step3 <- (str_extract_all(avg.calc.step2, "\\s\\d{1,2}"))
avg.calc.step3[16]
```

```{r}
matrix.calc <- matrix(unlist(avg.calc.step3), byrow=TRUE, nrow=length(avg.calc.step3) )
dim(matrix.calc)
```

```{r}
new.matrix <- t(apply(matrix.calc, 1,as.numeric)) 
dim(new.matrix)
```
### Data cleaning
```{r}
for (i in 1:nrow(new.matrix)) 
  {
  for (j in 1:ncol(new.matrix))
    {
    if (new.matrix[i,j] == 0){
      new.matrix[i,j] = NA
    }
    else{
      new.matrix[i,j] <- pre.rating[new.matrix[i,j]]
    }
  }
}
```

```{r}
avg.opponents <- c(rowMeans(new.matrix, na.rm = TRUE))

csv <- data.frame(player.name,player.state, player.points,pre.rating,avg.opponents)
colnames(csv) <- c("Player Name","Player State", "Total Points", "Player Pre-Rating", "Opponents Rating")
csv
```


### Export Data to CSV File
```{r}
write.csv(csv, "DATA_607_Project1.csv", row.names=FALSE)

```


