---
title: "How popular is Donald Trump before and after Convid-19?
"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

An calculation of the president's approval rating before convid19 and after convid19:
The link of article is provide as below
https://projects.fivethirtyeight.com/trump-approval-ratings/


### Step 1:
pulling data from online excel sheet
```{r }
polls <- read.csv('https://raw.githubusercontent.com/szx868/data607/master/approval_topline.csv')
head(polls)
```
### Step 2:
pick the columns you need, this case we only looking for date and approve estimate and disapprove estimate.

```{r}
polls <- polls[c('modeldate','approve_estimate','disapprove_estimate')]
head(polls)

```
### Step 3:
Convert modeldate column from chr to date, so we filter out data 
```{r}
polls$modeldate <- as.Date(polls$modeldate,
                                     format = "%m/%d/%y")

sorted.polls <- order(polls['modeldate'])
head(polls[sorted.polls,])


```

### Step 4:
Extract subset of data prior national emergency date(2020-03-13)
Extract subset of data after national emergency date(2020-03-13)


```{r}
polls.beforeConvid <- subset(polls,subset = modeldate<as.Date("2020-03-13"))
polls.afterConvid <- subset(polls,subset = modeldate>=as.Date("2020-03-13"))



```
### Step 5:
plot graph to visualize result
```{r}
library(ggplot2)

ggplot(data=polls.afterConvid, aes(x = modeldate, y = approve_estimate)) +
        geom_line() +
      labs(title = "Approval Rate Trend for After Convid")

```
```{r}
ggplot(data=polls.beforeConvid, aes(x = modeldate, y = approve_estimate)) +
        geom_line() +
      labs(title = "Approval Rate Trend for Before Convid")

```
### Step 6:
Renaming the columns to 'approve' and disapprove'
compare summary of two data frame

```{r}
polls.afterConvid <- polls.afterConvid[c('approve_estimate','disapprove_estimate')]
polls.beforeConvid <- polls.beforeConvid[c('approve_estimate','disapprove_estimate')]
colnames(polls.beforeConvid) <- c('approve', 'disappove')
colnames(polls.afterConvid) <- c('approve', 'disappove')
summary(polls.beforeConvid)
summary(polls.afterConvid)
```

### Conclusion

Based on those data it look like the popularity of Trump is not effected a lot by Convid-19 when you compare mean of Approve and mean of Disapprove. To have a more accurate result, I would recommend to take another static for different subgroup(Voters,All Polls, Adults)



