---
title: "Assignment7_ZhouxinShi"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

Pick three of your favorite books on one of your favorite subjects. At least one of the books should have more
than one author. For each book, include the title, authors, and two or three other attributes that you find
interesting.
```{r}
knitr::opts_chunk$set(warning=FALSE, 
                      message=FALSE,
                      tidy=F,
                      #comment = "",
                      dev="png", 
                      dev.args=list(type="cairo"))


#create vector with all needed packages
load_packages <- c("RCurl","prettydoc", "stringr", "dplyr", "knitr", "janitor", "XML", "tidyr", "RJSONIO")


t(t(sapply(load_packages, require, character.only = TRUE, quietly = TRUE,  warn.conflicts = FALSE)))
```


Step 1. HTML Table Parsing
Load data, look at the HTML table & then its data frame

```{r}
url_html <- getURLContent("https://raw.githubusercontent.com/szx868/data607/master/Assignment7/books2.html")


writeLines(url_html)
```
```{r}
my_html_df <- url_html %>% 
  readHTMLTable(header=TRUE, as.data.frame = TRUE) %>% 
  data.frame(stringsAsFactors = FALSE) %>% 
  clean_names() 

colnames(my_html_df) <- str_replace(colnames(my_html_df),"null_", "")
my_html_df <- my_html_df %>% arrange(desc(book_title))
kable(my_html_df)
```
Step 2. JSON Parsing
Load data, look at the JSON & then its data frame
```{r}
url_json <- getURLContent("https://raw.githubusercontent.com/szx868/data607/master/Assignment7/books.json")

print("Is my JSON valid?")
```

```{r}
isValidJSON("https://raw.githubusercontent.com/szx868/data607/master/Assignment7/books.json")
```
```{r}
writeLines(url_json)
```

```{r}
my_json_df <- fromJSON(url_json)

my_json_df <- do.call("rbind", lapply(my_json_df$`favorite recent books`, data.frame, stringsAsFactors = F))

my_json_df <- my_json_df %>%  
  clean_names() %>% 
  arrange(desc(book_title))

kable(my_json_df, caption = "data frame looks the same as the HTML one.")
```
Step 3. XML Parsing
Load data, look at the XML & then its data frame
```{r}
url_XML <- getURLContent("https://raw.githubusercontent.com/szx868/data607/master/Assignment7/books.xml")

writeLines(url_XML)
```
```{r}
my_XML_df <- url_XML %>% 
  xmlParse() %>% 
  xmlToDataFrame(stringsAsFactors = FALSE) 

kable(my_XML_df, caption = "This does not look the same as the first 2 data frames. For the book with more than one author, the function concatenated all of them into a single cell. Let's do a little bit of surgery to get the same result.")
```
```{r}
my_XML_df2 <- my_XML_df %>% 
  mutate(authors = paste(str_replace_all(authors, "([a-z])([A-Z])", "\\1,\\2"))) %>% 
  separate(authors, c(paste0("author_", 1:4)), sep = ",") %>% 
  gather(author_num, author, author_1:author_4, na.rm = T) %>% 
  select(book_title, author, everything(), -author_num) %>% 
  arrange(desc(book_title)) 
  
kable(my_XML_df2, caption = "And now it looks like the other 2 data frames")
```


```{r}
my_json_df == my_html_df

```
```{r}
my_html_df == my_XML_df2

```

