---
title: "Homework3_ZhouxinShi"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Please deliver links to an R Markdown file (in GitHub and rpubs.com) with solutions to the problems below.  You may work in a small group, but please submit separately with names of all group participants in your submission.

 **1. Using the 173 majors listed in fivethirtyeight.com’s College Majors dataset [https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/], provide code that identifies the majors that contain either "DATA" or "STATISTICS"**

```{r}
library(stringr)

college.majors <- read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/majors-list.csv",header=TRUE,stringsAsFactors=FALSE)

data <- str_detect(college.majors$Major, fixed("DATA"))
college.majors[data, ]
```
```{r}
stats <- str_detect(college.majors$Major, fixed("STATISTICS"))
college.majors[stats, ]
```


 **2. Write code that transforms the data below:**

```{r}
fruits <- '[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"

[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  

[9] "elderberry"   "lime"         "lychee"       "mulberry"    

[13] "olive"        "salal berry"'
fruits
```


```{r}
fruits_extract <- unlist(str_extract_all(fruits, pattern = "\"([a-z]+.[a-z]+)\""))
fruits_extract
```


```{r}
fruits_remove <- str_remove_all(fruits_extract, "\"")
fruits_remove
```


The two exercises below are taken from R for Data Science, 14.3.5.1 in the on-line version:

**3. Describe, in words, what these expressions will match:**

(.)\1\1

This will match any one character, followed by two repetitions, such as "ccc" or "111". The correct expression would be "(.)\\1\\1".

```{r}
str_match("ccc","(.)\\1\\1")

```

"(.)(.)\2\1"

This will search for two characters repeated, except reverse. Like "abba" or "1331".
The correct expression would be "(.)(.)\\2\\1".
```{r}
str_match("1331","(.)(.)\\2\\1")

```

(..)\1

This will search for two characters, repeated once, like "abab" or "7878". The correct expression would be "(..)\\1".
```{r}
str_match("7878","(..)\\1")

```


"(.).\1.\1"

This will search for a five character term, three of which are the same, like "cacdc" or "95929".The correct expression would be "(.).\\1.\\1".

```{r}
str_match("95929","(.).\\1.\\1")

```

"(.)(.)(.).*\3\2\1"

This will construct a set of characters that begin and end with the same three characters, except the second instance is reversed, like “abczegcba” or “1238879321”.
```{r}
str_match("abczegcba","(.)(.)(.).*\\3\\2\\1")

```


**4. Construct regular expressions to match words that:**

- Start and end with the same character.

"(.).*\\1"
```{r}
str_detect("abba","(.).*\\1")

```

- Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)

".*([A-Za-z][A-Za-z]).*\\1.*"

```{r}
str_detect("church",".*([A-Za-z][A-Za-z]).*\\1.*")

```
- Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.) 

".*([A-Za-z]).*\\1.\\1.*."

```{r}
str_detect("eleven",".*([A-Za-z]).*\\1.\\1.*")

```

